Har en persons høyde innvirkning på lønna?

### 2020-10-07 MSB105-Assignment-2-Katrine-Karl-Gunnar.Rmd
update
yaml update

---
title: "R Notebook"
output: html_notebook
---

```{r setup, echo=FALSE}

```

>>>>

---
title: "Har en persons høyde innvirkning på lønna?"
subtitle: "Assignment 2 i MSB105 Data Science - innleveringsfrist 12.10.20"
author: 
  - Katrine Hope
  - Karl-Gunnar Severinsen
classoption: twoside
fontsize: 12pt
linestretch: 1.5
output: html_notebook
---

```{r setup, echo = FALSE}
library(modelr)
library(ggplot2)
library(knitr)
library(tinytex)
library(tidyverse)
library(ggpubr)
library(dplyr)
```

## Introduksjon

## Analyse

## Referanser
